### 2017-12-06 submission/manuscript.Rmd
add reproducible research section and update acknowledgements

***Reproducible Methods:***
The code and analysis can be found here https://github.com/SchlossLab/Sze_PCRSeqEffects_XXXX_2017.

@@

The authors would like to thank all the study participants who were a part of each of the individual studies utilized. We would also like to thank each of the study authors for making their data available for use. Finally we would like to thank the members of the Schloss lab for valuable feed back and proof reading during the formulation of this manuscript.

>>>>

***Reproducible Methods:***
The code and analysis can be found here https://github.com/SchlossLab/Sze_PCRSeqEffects_XXXX_2017. The raw sequences can be found in the SRA at the following accesssion number **need to upload still**.

@@

The authors would like to thank all the study participants ERIN whose samples were utilized. We would also like to thank Judy Opp and April Cockburn for their effort in sequencing the samples as part of the Microbiome Core Facility at the University of Michigan. Salary support for Marc Sze came from the Canadian Institue of Health Research and the Michigan Institute for Clinical and Health Research Postdoctoral Translational Scholar Program.
